The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
refs

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index (SRI, Cairns and Schwager 1987): <!-- TODO: get Cairns ref-->

@@

Animal movement undoubtedly affects an individual's social environment
(Strandburg-Peshkin et al. 2015). Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al. 2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al. 2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g. Mourier et al. 2019).

>>>>

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): <!-- TODO: get Cairns ref-->

@@

Animal movement undoubtedly affects an individual's social environment
[@Strandburg-Peshkin2015]. Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al. 2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al. 2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g. Mourier et al. 2019).
